---
title: "Worker Script Report: Update Rainfall Tables"
author:
- Taylor Heffernan
- Updating rainfall_gage
date: "`r lubridate::now()`" #This doesn't use !r syntax (like the gagedb param below) because it's not a param. It's evaluated by default.
output: html_document
params:
  gagedb: !r paste0(path.expand('~'), '/CSORain2010/CSORain2010.mdb') #Access DB containing rain gage data. !r evaluates the R expression. Doesn't use `r` syntax like the date flag above because params are treated as plain text (not evaluated) by default. 
  database: "mars_testing" #One of mars or mars_testing. Requires a DSN of the same name.
  write: FALSE #Write changes to database?
---

```{r setup, include=FALSE}

#Dplyr stuff
library(magrittr)
library(tidyverse)
library(lubridate)

#Database Stuff
library(odbc)
library(RODBC)

#Other stuff
library(knitr)
options(stringsAsFactors=FALSE)
```

```{r Section 0 - Preamble and database connections, include=FALSE}
###Section 0.1: Check parameter validity

###Section 0.2: Connect to the database
	#Indicate the database name: mars_testing or mars. 
	#Only write to mars if you really know what you're doing.
 	database <- params$database

 	#Connect using the DSN.
	marsDBCon <- dbConnect(odbc::odbc(), params$database)

###Section 0.3: Load MARS analysis functions
	source("A:/Scripts/Functions/mars_functions.R")
	
```
  

```{r Section 1 - Gathering rainfall data, include = FALSE}

  #Read the rain gage data from the mars database
  rainfall_gage <- dbGetQuery(marsDBCon, "SELECT * FROM rainfall_gage")  
  
  #Read the rain gage table from the mars database and attach it to the rainfall data
  gage <- dbGetQuery(marsDBCon, "SELECT * FROM gage")
  rainfall_gage <- left_join(rainfall_gage, gage, by = "gage_uid")
  
  #Read the rain gage data from the H&H database
  hhdbcon <- odbcConnectAccess2007(params$gagedb)
  hhrainfall_gage <- sqlFetch(hhdbcon, "tblModelRain", as.is = TRUE)
  hhrainfall_gage %<>% transmute(gagename = as.character(GaugeNo), dtime_edt = ymd_hms(DateTime), rainfall_in = Rainfall)
  odbcClose(hhdbcon)
  
  newdata <- anti_join(hhrainfall_gage, rainfall_gage, by = c("gagename", "dtime_edt")) %>%
    left_join(gage, by = "gagename") %>%
    select(gage_uid, dtime_edt, rainfall_in)

```


## Updates to `rainfall_gage` Table

A new batch of rainfall data has been examined. There are `r nrow(newdata)` new rainfall measurements to add to the `rainfall_gage` table.

`r if(nrow(newdata) > 0){ group_by(newdata, gage_uid) %>% summarize(new_measurements = n()) %>% kable }`

```{r Section 1.5 - Writing to the smp_loc table, include = FALSE}	
# Fail safe. If the block below doesn't run, we didn't append anything
  outcome_newdata <- FALSE

  #If there's new data to append
	if(nrow(newdata) > 0 & params$write == TRUE){
    outcome_newdata <- tryCatch({outcome_newdata <- dbWriteTable(marsDBCon, 
        "rainfall_gage", 
        newdata, 
        append= TRUE, 
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }
```
  
`r if(nrow(newdata) > 0){ paste("New rain events have", ifelse(outcome_newdata, "SUCCESSFULLY", "NOT"), "been written to the rainfall_gage table")}`

```{r Section 2 - Processing new rain events, include = FALSE}

  #Read the rain gage data from the mars database
  #This query will grab all data from after the end of the latest event for each gage
  #This captures both new data appended in the previous section, and any data that was clipped last time events were processed
  newrain_query <- "select rg.gage_uid, rg.dtime_edt, rg.rainfall_in from rainfall_gage rg left join rainfall_gage_event_latestdates rgel on rg.gage_uid = rgel.gage_uid where rg.dtime_edt > rgel.dtime_edt"
  rain_newdata <- dbGetQuery(marsDBCon, newrain_query)

  #If we aren't writing the new data to the database, the above won't capture this batch of rain data
  #Append the newdata frame to the above thing
  if(params$write == FALSE){
    rain_newdata <- bind_rows(rain_newdata, newdata) %>% arrange(gage_uid, dtime_edt)
  }
  
  #If there's no defined rain events, that query will return nothing
  #So we need to grab the entire data set
  emptytable <- dbGetQuery(marsDBCon, "select count(*) from rainfall_gage_event_latestdates") %>% pull(count)
  if(emptytable == 0){
    rain_newdata <- dbGetQuery(marsDBCon, "select dtime_edt, gage_uid, rainfall_in from rainfall_gage")
  }
  
  #Process the rain data into events, based on a 6 hour interevent time and a minimum depth of 0.1 inches
  rain_newevents <- rain_newdata %>% 
    group_by(gage_uid) %>%
    arrange(dtime_edt) %>% 
    mutate(event_id = detectEvents(dtime_edt, rainfall_in)) %>%
      #Drop the last "complete" event in case it straddles the month boundary
      #It will get processed the when the next batch of data comes in
    filter(!is.na(event_id), event_id != max(event_id, na.rm = TRUE)) %>%
    group_by(gage_uid, event_id) %>%
    summarize(eventdatastart_edt = first(dtime_edt),
      eventdataend_edt = last(dtime_edt),
      eventduration_hr = stormDuration_hr(dtime_edt),
      eventpeakintensity_inhr = stormPeakIntensity_inhr(dtime_edt, rainfall_in),
      eventavgintensity_inhr = stormAvgIntensity_inhr(dtime_edt, rainfall_in),
      eventdepth_in = stormDepth_in(rainfall_in)) %>%
    select(-event_id)

```


## Updates to `rainfall_gage_event` Table

The latest rainfall data has been processed for event detection. There are `r nrow(rain_newevents)` new rain events to add to the `rainfall_gage_event` table.

`r if(nrow(rain_newevents) > 0){ rain_newevents %>% head(100) %>% kable }`

```{r Section 2.5 - Writing to the smp_loc table, include = FALSE}  
# Fail safe. If the block below doesn't run, we didn't append anything
  outcome_rain_newevents <- FALSE

  #If there's new data to append
  if(nrow(rain_newevents) > 0 & params$write == TRUE){
    outcome_rain_newevents <- tryCatch({outcome_rain_newevents <- dbWriteTable(marsDBCon, 
        "rainfall_gage_event", 
        rain_newevents, 
        append= TRUE, 
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }
```

`r if(nrow(rain_newevents) > 0){ paste("New rain events have", ifelse(outcome_rain_newevents, "SUCCESSFULLY", "NOT"), "been written to the rainfall_gage_event table")}`

```{r Section 3 - Close DB connections and render this file, include = FALSE}
	#Close database connections
	dbDisconnect(marsDBCon)
```
