---
title: "Maintenance Script Report: Update Rainfall Tables"
author:
- Taylor Heffernan and Nick Manna
- Updating rainfall_gage
date: "`r lubridate::now()`" #This doesn't use !r syntax (like the gagedb param below) because it's not a param. It's evaluated by default.
output: html_document
params:
  database: "mars_testing" #One of mars or mars_testing. Requires a DSN of the same name.
  write: TRUE #Write changes to database?
---

```{r setup, include=FALSE}
#Database Stuff
library(odbc)
library(tidyverse)
library(lubridate)
library(pwdgsi)
library(sf)
library(padr)

#Other stuff
library(knitr)
options(stringsAsFactors=FALSE)
```

```{r Section 0 - Preamble and database connections, include=FALSE}
###Section 0.1: Check parameter validity
	if(!(params$database %in% c("mars", "mars_testing"))){
		stop(paste("Invalid database parameter:", params$database))
	}

###Section 0.2: Connect to the database
	#Indicate the database name: mars_testing or mars. 
	#Only write to mars if you really know what you're doing.
	marsDBCon <- dbConnect(odbc::odbc(), params$database)
	
```

```{r Section 1 - Gathering rainfall data, include = FALSE}
  #Read the rain gage data from the mars database
  rainfall_gage <- dbGetQuery(marsDBCon, "SELECT * from rainfall_gage_latestdates")  
  
  #Read the rain gage table from the mars database and attach it to the rainfall data
  gage <- dbGetQuery(marsDBCon, "SELECT * FROM gage")
  rainfall_gage <- left_join(rainfall_gage, gage, by = "gage_uid") %>% select(gagename, maxtime_edt)
  
  #Read the rain gage data from the H&H database
  hhdbcon <- dbConnect(odbc::odbc(), "CentralDB")
  hhrainfall_gage <- dbGetQuery(hhdbcon, "select * from pwdrg.tblModelRain") %>% 
    transmute(gagename = as.character(GaugeNo), dtime_edt = force_tz(ymd_hms(DateTime), "America/New_York"), rainfall_in = Rainfall)
  dbDisconnect(hhdbcon)
  
  newdata <- hhrainfall_gage %>% 
    left_join(rainfall_gage, by = "gagename") %>% 
    group_by(gagename) %>%
    filter(dtime_edt > maxtime_edt) %>%
    ungroup %>%
    select(gagename, dtime_edt, rainfall_in) %>%
    left_join(gage, by = "gagename") %>%
    select(gage_uid, dtime_edt, rainfall_in) %>%
    arrange(gage_uid, dtime_edt)
  
```

## Updates to `rainfall_gage` Table

A new batch of rainfall data has been examined. There are `r nrow(newdata)` new rainfall measurements to add to the `rainfall_gage` table.

`r if(nrow(newdata) > 0){ group_by(newdata, gage_uid) %>% arrange(dtime_edt) %>% summarize(new_measurements = n(), first_date = first(dtime_edt), last_date = last(dtime_edt)) %>% kable }`

```{r Section 1.5 - Writing to the smp_loc table, include = FALSE}	
  # Fail safe. If the block below doesn't run, we didn't append anything
  outcome_newdata <- FALSE

  #If there's new data to append
  	if(nrow(newdata) > 0 & params$write == TRUE){
      outcome_newdata <- tryCatch({outcome_newdata <- dbWriteTable(marsDBCon,
          "rainfall_gage_raw",
          newdata,
          append= TRUE,
          row.names = FALSE)
        }, # append the data
        error = function(e) e
      )
  }
```

`r if(nrow(newdata) > 0){ paste("New rain events have", ifelse(outcome_newdata, "SUCCESSFULLY", "NOT"), "been written to the rainfall_gage table")}`

```{r Section 2 - Processing new rain events, include = FALSE}
  #Read the rain gage data from the mars database
  #This query will grab all data from after the end of the latest event for each gage
  #This captures both new data appended in the previous section, and any data that was clipped last time events were processed
  newrain_query <- "select rg.gage_uid, rg.dtime_edt, rg.rainfall_in from rainfall_gage rg left join rainfall_gage_event_latestdates rgel on rg.gage_uid = rgel.gage_uid where rg.dtime_edt > rgel.dtime_edt"
  rain_newdata <- dbGetQuery(marsDBCon, newrain_query)
  #If we aren't writing the new data to the database, the above won't capture this batch of rain data
  #Append the newdata frame to the above thing
  if(params$write == FALSE){
    rain_newdata <- bind_rows(rain_newdata, newdata) %>% arrange(gage_uid, dtime_edt)
  }
  
  #If there's no defined rain events, that query will return nothing
  #So we need to grab the entire data set
  emptytable <- dbGetQuery(marsDBCon, "select count(*) from rainfall_gage_event_latestdates") %>% pull(count)
  if(emptytable == 0){
    rain_newdata <- dbGetQuery(marsDBCon, "select dtime_edt, gage_uid, rainfall_in from rainfall_gage")
  }
  
  #Process the rain data into events, based on a 6 hour interevent time and a minimum depth of 0.1 inches
  rain_newevents <- rain_newdata %>% 
    group_by(gage_uid) %>%
    arrange(dtime_edt) %>% 
    mutate(event_id = marsDetectEvents(dtime_edt, rainfall_in)) %>%
      #Drop the last "complete" event in case it straddles the month boundary
      #It will get processed the when the next batch of data comes in
    filter(!is.na(event_id), event_id != max(event_id, na.rm = TRUE)) %>%
    group_by(gage_uid, event_id) %>%
    summarize(eventdatastart_edt = first(dtime_edt),
      eventdataend_edt = last(dtime_edt),
      eventduration_hr = marsStormDuration_hr(dtime_edt),
      eventpeakintensity_inhr = marsStormPeakIntensity_inhr(dtime_edt, rainfall_in),
      eventavgintensity_inhr = marsStormAverageIntensity_inhr(dtime_edt, rainfall_in),
      eventdepth_in = marsStormDepth_in(rainfall_in)) %>%
    select(-event_id)
```


## Updates to `rainfall_gage_event` Table

The latest rainfall data has been processed for event detection. There are `r nrow(rain_newevents)` new rain events to add to the `rainfall_gage_event` table.

`r if(nrow(rain_newevents) > 0){ rain_newevents %>% head(100) %>% kable }`

```{r Section 2.5 - Writing to the smp_loc table, include = FALSE}  
# Fail safe. If the block below doesn't run, we didn't append anything
  outcome_rain_newevents <- FALSE
  #If there's new data to append
  if(nrow(rain_newevents) > 0 & params$write == TRUE){
    outcome_rain_newevents <- tryCatch({outcome_rain_newevents <- dbWriteTable(marsDBCon, 
        "rainfall_gage_event", 
        rain_newevents, 
        append= TRUE, 
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }
```

`r if(nrow(rain_newevents) > 0){ paste("New rain events have", ifelse(outcome_rain_newevents, "SUCCESSFULLY", "NOT"), "been written to the rainfall_gage_event table")}`

```{r Section 3 - Gathering radar data, include = FALSE}
  
  hhdbcon <- dbConnect(odbc::odbc(), "CentralDB")

  #Assess raw files in our DB and H&H
  db_rawfiles <- dbGetQuery(marsDBCon, "select * from public.radarcell_rawfile")
  hh_rawfiles <- dbGetQuery(hhdbcon, "select yearmon, path as filepath from radar2sheds.garr_inventory") %>%
    mutate(yearmon = str_replace(yearmon, "-", "")) %>%
    mutate(filepath = str_replace(filepath, "\\\\", "/")) %>%
    mutate(filepath = str_replace(filepath, "M:/", "//pwdoows/OOWS/Modeling/"))
  dbDisconnect(hhdbcon)

  #Which files don't we have
  new_rawfiles <- filter(hh_rawfiles, !(filepath %in% db_rawfiles$filepath))
  
  #only cells in Philly
  phillycells <- dbGetQuery(marsDBCon, "select radarcell_uid from radarcell")
  
  #Unzip the files
  dir.create("~/radarrain", showWarnings = FALSE)
  for(i in 1:nrow(new_rawfiles)){
    if(nrow(new_rawfiles) == 0){break}
    file.copy(from = new_rawfiles$filepath[i], to = "~/radarrain", overwrite = FALSE)
    unzip(paste0("~/radarrain/", basename(new_rawfiles$filepath[i])), exdir = "~/radarrain", files = paste0(new_rawfiles$yearmon[i], ".csv"))
    file.remove(paste0("~/radarrain/", basename(new_rawfiles$filepath[i])))
  }
  
  #read the files
  newradarfiles <- list.files(path = "~/radarrain", full.names = TRUE, pattern = "\\.csv$")
  newradardata <- data.frame(dtime_edt = NULL, radarcell_uid = NULL, rainfall_in = NULL)
  for(i in 1:length(newradarfiles)){
    if(length(newradarfiles) == 0){break}
    print(paste0("reading ", newradarfiles[i]))
    radarfile <- read.csv(newradarfiles[i], header = FALSE)
    colnames(radarfile) <- c("dtime_raw", "tz", "radarcell_uid", "rainfall_in")
    radarfile <- radarfile %>% 
      filter(radarcell_uid %in% phillycells$radarcell_uid) %>%
      transmute(dtime_edt = ymd_hm(dtime_raw, tz = "America/New_York"), radarcell_uid, rainfall_in)
   
    radarinterval <- get_interval(radarfile$dtime_edt)
    print(paste("File", basename(newradarfiles[i]), "has datetime interval", radarinterval))
  
    if(radarinterval != "15 min"){
      radarfile <- thicken(radarfile, "15 min", rounding = "up", ties_to_earlier = TRUE) %>%
        group_by(dtime_edt_15_min, radarcell_uid) %>%
        summarize(rainfall_in = sum(rainfall_in)) %>%
        select(dtime_edt = dtime_edt_15_min, radarcell_uid, rainfall_in)
    }

    radarfile <- filter(radarfile, rainfall_in > 0)
       
    newradardata <- bind_rows(newradardata, radarfile)
    file.remove(newradarfiles[i])
  }
  
```

```{r Section 3.5 - Writing to the radarcell tables, include = FALSE}  
# Fail safe. If the block below doesn't run, we didn't append anything
  outcome_rawfiles <- FALSE
  #If there's new data to append
  if(nrow(new_rawfiles) > 0 & params$write == TRUE){
    new_rawfiles <- select(new_rawfiles, -yearmon)
    outcome_rawfiles <- tryCatch({outcome_rawfiles <- dbWriteTable(marsDBCon, 
        "radarcell_rawfile", 
        new_rawfiles, 
        append= TRUE, 
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }

  outcome_radardata <- FALSE
  #If there's new data to append
  if(nrow(newradardata) > 0 & params$write == TRUE){
    outcome_radardata <- tryCatch({outcome_radardata <- dbWriteTable(marsDBCon, 
        "rainfall_radarcell_raw", 
        newradardata, 
        append= TRUE, 
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }

```

```{r Section 4 - Processing new rain events for radarcell data, include = FALSE}
  #Read the radarcell data from the mars database
  #This query will grab all data from after the end of the latest event for each cell
  #This captures both new data appended in the previous section, and any data that was clipped last time events were processed

  #process cells one at a time
  allcells <- dbGetQuery(marsDBCon, "select distinct radarcell_uid from radarcell")

    newrain_query <- paste("select rc.radarcell_uid, rc.dtime_edt, rc.rainfall_in from rainfall_radarcell_raw rc left join rainfall_radarcell_event_latestdates rcel on rc.radarcell_uid = rcel.radarcell_uid where rc.dtime_edt > rcel.dtime_edt")

    
  rain_newdata <- dbGetQuery(marsDBCon, newrain_query)  
    
  print(paste(nrow(rain_newdata), "data points"))
    
    #Process the rain data into events, based on a 6 hour interevent time and a minimum depth of 0.1 inches
    rain_newevents <- rain_newdata %>% 
      group_by(radarcell_uid) %>%
      arrange(dtime_edt) %>% 
      mutate(event_id = marsDetectEvents(dtime_edt, rainfall_in)) %>%
      #Drop the last "complete" event in case it straddles the month boundary
      #It will get processed the when the next batch of data comes in
      filter(!is.na(event_id), event_id != max(event_id, na.rm = TRUE)) %>%
      group_by(radarcell_uid, event_id) %>%
      summarize(eventdatastart_edt = first(dtime_edt),
                eventdataend_edt = last(dtime_edt),
                eventduration_hr = marsStormDuration_hr(dtime_edt),
                eventpeakintensity_inhr = marsStormPeakIntensity_inhr(dtime_edt, rainfall_in),
                eventavgintensity_inhr = marsStormAverageIntensity_inhr(dtime_edt, rainfall_in),
                eventdepth_in = marsStormDepth_in(rainfall_in)) %>% 
      select(-event_id)
      
      print(paste(nrow(rain_newevents), "new events"))
    
  
```

```{r Section 4.5 - Writing to the rainfall_radarcell_event table, include = FALSE}  
# Fail safe. If the block below doesn't run, we didn't append anything
  outcome_rain_newevents <- FALSE
  #If there's new data to append
  if(nrow(rain_newevents) > 0 & params$write == TRUE){
    outcome_rain_totalevents <- tryCatch({outcome_rain_newevents <- dbWriteTable(marsDBCon, 
        "rainfall_radarcell_event", 
        rain_newevents, 
        append= TRUE, 
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }
```

```{r Section 3 - Close DB connections and render this file, include = FALSE}
	#Close database connections
	dbDisconnect(marsDBCon)
```