---
title: "Maintenance Script Report: Backing up the MARS Analysis Database"
author:
- Taylor Heffernan
- Backing up the `r params$database` database
date: "`r lubridate::now()`"
output: html_document
params:
  database: "mars_testing" #One of mars or mars_testing. Requires a DSN of the same name.
---

```{r setup, include=FALSE}

#Dplyr stuff
library(magrittr)
library(tidyverse)
library(lubridate)

#Database Stuff
library(odbc)

#Other stuff
library(knitr)
library(openssl)
options(stringsAsFactors=FALSE)
```

```{r Section 0 - Preamble , include=FALSE}
###Section 0.1: Set filename parameters
	#Standard timestamp format found on Stack Overflow
		#%Y: 4 digit year [1:4]
		#%m: 2 digit month [5:6]
		#%d: 2 digit day [7:8]
		#%H: 2 digit 24h hour [10:11]
		#%M: 2 digit month [12:13]
		#%S: 2 digit second [14:15]
	datestring <- Sys.time() %>% format("%Y%m%dT%H%M")
	extension <- "pgdump"
	
###Section 0.2: set pg_dump parameters
  #User to perform the dump (-U)
	#Can't dump with mars_readonly because it will not have access to the ODBC user mappings for the foreign tables
	#No password is asked for because it's contained in our pgpass.conf file
	dump_user <- "postgres"

	#Additional parameters
		#-Fc: Custom archive format - create a compressed archive suitable for pg_restore
	dump_params <- "-Fc"
	
###Section 0.3: Set pg_restore parameters
	#Test DB name tag
	restorename <- "archivetest"
	
	#Additional parameters
	  #-j5: Restore the database 5 tables at a time, which is much faster
	restore_params <- "-j5"
	
```
  

```{r Section 1 - Back up the database to the W drive, include = FALSE}
  
  #W drive filepath
  drive_letter <- "W"
	filename <- paste0(datestring, "_", params$database, ".", extension)
  filepath <- paste0(drive_letter, ":\\marsbackup/", params$database, "/", filename)

  #Assemble the entire pg_dump	
	pgdumpstring <- paste("pg_dump", 
  	"-U", dump_user,
  	dump_params,
  	params$database,
  	">", filepath)
	
	results_dump <- shell(pgdumpstring, intern = TRUE)

```


## Backing up the `r params$database` database to the W drive

The `r params$database` database was `r ifelse(length(results_dump) == 0, "SUCCESSFULLY", "NOT")` backed up to the W drive.

`r if(length(results_dump) == 0){ paste("The file is located at", gsub("\\\\", "/", filepath)) }`

---

```{r Section 2 - Restoring the W drive backup, include = FALSE}	

  #Compose test name for the restored database
  testdatabase <- paste(drive_letter, "archivetest", params$database, datestring, sep = "_")
  
  #PG_Restore the archive at `filepath` back to the database with the test name
  #Create the string that will be used to create the db
  createdbstring <- paste("createdb",
    "-U", dump_user,
    "-T template0", #Template0 is a blank database
    testdatabase)
  
  #Create that database
  results_createdb <- shell(createdbstring, intern = TRUE)

  #Compose pg_restore command string
  pgrestorestring <- paste("pg_restore",
    "-U", dump_user,
    restore_params,
    "-d", testdatabase,
    filepath)
  
  #Restore the archived database
  results_restore <- shell(pgrestorestring, intern = TRUE)

```
  
  
## Creating the scratch database to test the backup

The scratch database, was `r ifelse(length(results_createdb) == 0, "SUCCESSFULLY", "NOT")` created on the MARS postgres server.  
  
`r if(length(results_createdb) == 0){ paste("The database is named", testdatabase) }`  
  
The scratch database was `r ifelse(length(results_restore) == 0, "SUCCESSFULLY", "NOT")` populated by the database archive located at `r gsub("\\\\", "/", filepath)`.

---
  
```{r Section 3 - Verifying the W drive backup, include = FALSE}

  ############################
  # Incomplete!
  ############################

  # #Read all tables in each database (backup and live) and verify they're the same
  # liveDBCon <- dbConnect(odbc(), params$database)
  # 
  # #Assemble all tables in the live database (params$database)
  #   #Tables we need to check for their integrity are non-foreign, non-matview tables
  # livetables <- list()
  # livetables$table <- dbListTables(liveDBCon, table_type = "table")
  # livetables$foreign <- dbListTables(liveDBCon, table_type = "foreign table")
  # livetables$matview <- dbListTables(liveDBCon, table_type = "matview")
  # livetables$regulartables <- setdiff(livetables$table, c(livetables$foreign, livetables$matview)) 
  # 
  # #Repeat that process for the test database
  # testDBCon <- dbConnect(odbc(), 
  #   server = "28-ARATHEFFE2.water.gov", 
  #   driver = "PostgreSQL Unicode(x64)", 
  #   database = testdatabase, 
  #   uid = "mars_readonly", 
  #   pwd = "ihatepostgrespermissions",
  #   port = "5432")
  # 
  # #Assemble all tables in the live database (params$database)
  #   #Tables we need to check for their integrity are non-foreign, non-matview tables
  # testtables <- list()
  # testtables$table <- dbListTables(testDBCon, table_type = "table")
  # testtables$foreign <- dbListTables(testDBCon, table_type = "foreign table")
  # testtables$matview <- dbListTables(testDBCon, table_type = "matview")
  # testtables$regulartables <- setdiff(testtables$table, c(testtables$foreign, testtables$matview)) 
  
  
  # #Match the contents of each table against each other, to see if they are identical
  # #Doing that hash business
  # # https://www.periscopedata.com/blog/hashing-tables-to-ensure-consistency-in-postgres-redshift-and-mysql
  # tables_identical <- NA
  # 
  # for(neverdothis in 1){
  #   #If the list of tables in each DB aren't the same, then don't bother with the rest of this stuff
  #   if(!identical(testtables$regulartables, livetables$regulartables)){
  #     tables_identical <- FALSE
  #     break
  #   }
  #   
  #   #iterate along tables and compose hash queries
  #   for(i in 1:length(livetables$regulartables)){
  #     table_info <- dbGetQuery(liveDBCon, paste0("select table_name, column_name, data_type from information_schema.columns where table_name = '", livetables$regulartables[i], "'::text"))
  #     
  #     
  #   }
  # }
  # 
    
```

```{r Section 3 - Back up the database to the X drive, include = FALSE}
  
  #W drive filepath
  drive_letter <- "X"
	filename <- paste0(datestring, "_", params$database, ".", extension)
  filepath <- paste0(drive_letter, ":\\marsbackup/", params$database, "/", filename)

  #Assemble the entire pg_dump	
	pgdumpstring <- paste("pg_dump", 
  	"-U", dump_user,
  	dump_params,
  	params$database,
  	">", filepath)
	
	results_dump <- shell(pgdumpstring, intern = TRUE)

```


## Backing up the `r params$database` database to the X drive

The `r params$database` database was `r ifelse(length(results_dump) == 0, "SUCCESSFULLY", "NOT")` backed up to the W drive.

`r if(length(results_dump) == 0){ paste("The file is located at", gsub("\\\\", "/", filepath)) }`

---

```{r Section 4 - Restoring the X drive backup, include = FALSE}	

  #Compose test name for the restored database
  testdatabase <- paste(drive_letter, "archivetest", params$database, datestring, sep = "_")
  
  #PG_Restore the archive at `filepath` back to the database with the test name
  #Create the string that will be used to create the db
  createdbstring <- paste("createdb",
    "-U", dump_user,
    "-T template0", #Template0 is a blank database
    testdatabase)
  
  #Create that database
  results_createdb <- shell(createdbstring, intern = TRUE)

  #Compose pg_restore command string
  pgrestorestring <- paste("pg_restore",
    "-U", dump_user,
    restore_params,
    "-d", testdatabase,
    filepath)
  
  #Restore the archived database
  results_restore <- shell(pgrestorestring, intern = TRUE)

```
  
  
## Creating the scratch database to test the backup

The scratch database, was `r ifelse(length(results_createdb) == 0, "SUCCESSFULLY", "NOT")` created on the MARS postgres server.  
  
`r if(length(results_createdb) == 0){ paste("The database is named", testdatabase) }`  
  
The scratch database was `r ifelse(length(results_restore) == 0, "SUCCESSFULLY", "NOT")` populated by the database archive located at `r gsub("\\\\", "/", filepath)`.

---
