---
title: "Worker Script Report: Update Baro Tables"
author:
- Taylor Heffernan
- Updating baro and baro_rawfile
date: "`r lubridate::now()`"
output: html_document
params:
  database: "mars_testing" #One of mars or mars_testing. Requires a DSN of the same name.
  write: FALSE #Write changes to database?
---

```{r setup, include=FALSE}

#Dplyr stuff
library(magrittr)
library(tidyverse)
library(lubridate)

#Database Stuff
library(odbc)

#Other stuff
library(knitr)
library(openssl)
options(stringsAsFactors=FALSE)
```



```{r Section 0 - Preamble and database connections, include=FALSE}
###Section 0.1: Check parameter validity

###Section 0.2: Connect to the database using the DSN.
	marsDBCon <- dbConnect(odbc::odbc(), params$database)

###Section 0.3: Helper function to find the first date in a file
  #Firstdate function reads a few lines of the file and finds a date at (or near) the top of the file
  firstdate <- function(datafile){
    dates <- sapply(datafile, FUN = function(x){
      temp <- read.csv(x, skip = 1, nrows = 5)
      temp <- temp[, 2:4]
      colnames(temp) <- c("dtime_est", "pres_psi", "temp_f")
      return(temp$dtime_est[1])
    })
    names(dates) <- NULL
    return(dates)
  }
	
```
  

```{r Section 1 - Gathering baro data, include = FALSE}

  #Fetch all host folders for baro data
  baro_rawfolders <- dbGetQuery(marsDBCon, "SELECT * FROM public.baro_rawfolder")

  #Fetch all the baro raw file paths that are currently in the database
  existingfiles <- dbGetQuery(marsDBCon, "SELECT * FROM public.baro_rawfile")
  
  #Fetch all of the latest dates for every baro in the baro table
  latestdates <- dbGetQuery(marsDBCon, "SELECT r.smp_id, max(b.dtime_est) as latestdate_est FROM public.baro b LEFT JOIN baro_rawfile r ON b.baro_rawfile_uid = r.baro_rawfile_uid GROUP BY smp_id")
  
  #If there are no dates, fake it with a date of January 1st, 2001
  latestdates <- left_join(baro_rawfolders, latestdates, by = "smp_id")
  latestdates$latestdate_est[is.na(latestdates$latestdate_est)] <- ymd_hms("2001-01-01 00:00:00 EST")

  #Search for all CSV files that say "baro" within those folders
  #Attach the smp_id from the associated raw folder to each path so we know which baro they belong to
  foundfiles <- NULL
  for(i in 1:nrow(baro_rawfolders)){
    files <- list.files(baro_rawfolders$folderpath[i], pattern = "baro.*csv$", full.names = TRUE, recursive = TRUE, ignore.case = TRUE) 

    if(length(files) == 0){
      break #If there is no baro data to be found, skip that folder
    }
    
    tempfiles <- data.frame(filepath = files, smp_id = baro_rawfolders$smp_id[i]) %>%
      filter(!grepl("SRT", filepath, ignore.case = TRUE))
    foundfiles <- rbind(foundfiles, tempfiles)
  }

  #Compute a variety of things relevant to the database
  #First, whether the file is already in the database
  filetable <- mutate(foundfiles, in_db = (filepath %in% existingfiles$filepath)) %>% 
    
    #filter to only those files not in the database
    filter(in_db == FALSE) %>% 

    #Find the first date in the files
    mutate(firstdate_est = mdy_hms(firstdate(filepath), tz = "EST")) %>% 

    #Filter to only the new stuff
    filter(firstdate_est >= ymd("2018-05-01", tz = "EST")) %>% 

    #Join them to the data frame showing the latest date for each baro in the database
    left_join(latestdates, by = "smp_id") %>%

    #Filter to only the files whose data are newer than the data in the database
    #This is necessary because some sites have multiple baros, and the database uses only one
    #So there can be files not in the rawfile table whose data is not relevant to us
    filter(firstdate_est > latestdate_est)

```


## Updates to `baro_rawfile` Table

The filesystem has been examined for new barometric pressure data. There are `r nrow(filetable)` new files containing relevant barometric pressure data.

`r filetable %>% transmute(filename = basename(filepath), smp_id, firstdate_est) %>% kable`

```{r Section 1.5 - Writing to the baro_rawfile table, include = FALSE}	
  #First, compute hashes and add files to the rawfile table (to get their UIDs)
  newrawfiles <- transmute(filetable,
    smp_id,
    filepath, 
    md5hash = sapply(X = filepath, FUN = function(x) as.character(md5(file(x)))))

  #sapply will give names to the elements of the column, which we don't want
  names(newrawfiles$md5hash) <- NULL

  # Fail safe. If the block below doesn't run, we didn't append anything
  outcome_newrawfiles <- FALSE

  #If there's new data to append
	if(nrow(newrawfiles) > 0 & params$write == TRUE){
    tryCatch({outcome_newrawfiles <- dbWriteTable(marsDBCon, 
        "baro_rawfile", 
        newrawfiles, 
        append= TRUE, 
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }
```

`r if(nrow(newrawfiles) > 0){ paste("New baro data files have", ifelse(outcome_newrawfiles, "SUCCESSFULLY", "NOT"), "been written to the baro_rawfile table")}`  
  
```{r Section 2 - Gathering the baro data, include = FALSE}

  #Collect the table of baro files again to find their UID
  existingfiles <- dbGetQuery(marsDBCon, "SELECT * FROM baro_rawfile")
  newfiles <- left_join(filetable, existingfiles, by = "filepath") %>% select(filepath, baro_rawfile_uid)

  #Gather the data from each new file
  newdata <- data.frame(dtime_est = NULL, baro_psi = NULL, temp_f = NULL, baro_rawfile_uid = NULL)

  for(i in 1:nrow(newfiles)){
    
    if(nrow(newfiles) == 0) {break} #Don't do anything if there are no files
    
    tempdata <- read.csv(newfiles$filepath[i], skip = 1)
    tempdata <- tempdata[, 2:4]
    colnames(tempdata) <- c("dtime_est", "baro_psi", "temp_f")
    tempdata$dtime_est <- mdy_hms(tempdata$dtime_est)
    tempdata$baro_rawfile_uid <- newfiles$baro_rawfile_uid[i]
    tempdata <- tempdata[complete.cases(tempdata[, 1:3]),] #Purge NA rows from the final data set

    newdata <- bind_rows(newdata, tempdata)
}
    
```
  

## New baro data
  
The `r nrow(newfiles)` new baro files contained `r nrow(newdata)` new data points.

`r if(nrow(newdata) > 0){ newdata %>% group_by(baro_rawfile_uid) %>% summarize(data_points = n(), first_est = first(dtime_est), last_est = last(dtime_est)) %>% kable }`

```{r Section 2.5, Writing to the baro table, include = FALSE}
  #Fail Safe. If the code block below doesn't run, we didn't append anything
  outcome_newdata <- FALSE

    if(nrow(newdata) > 0 & params$write == TRUE){
    tryCatch({outcome_newdata <- dbWriteTable(marsDBCon, 
        "baro", 
        newdata, 
        append= TRUE, 
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }

```

`r if(nrow(newdata > 0)){ paste("New baro data has", ifelse(outcome_newdata, "SUCCESSFULLY", "NOT"), "been written to the baro table")}`

```{r Section 3 - Close DB connections and render this file, include = FALSE}
	#Close database connections
	dbDisconnect(marsDBCon)
```
