---
title: "PG14_back_up"
author: "Farshad Ebrahimi"
date: "`r lubridate::now()`"
output: html_document
params:
  database: "mars14_data" 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Dplyr stuff
  library(magrittr)
  library(tidyverse)
  library(lubridate)

#Database Stuff
  library(odbc)
  library(DBI)

#Other stuff
  library(openssl)
  library(knitr)
  options(stringsAsFactors=FALSE)
  


```

```{r Section 1 - Back up , include = FALSE}
## Back up the database   
#which database to backup? what format?
  format_archive <- "c"
  format <- paste("--format=",format_archive, sep = "")
  database_archive <-"mars_data"
  db <- paste("--dbname=",shQuote(database_archive), sep ="")
  
#specify other details: the pathway to find pg_dump, where to save archive, naming format, database server specs, and username credentials  
  datestring <- Sys.time() %>% format("%Y%m%dT%H%M")
  extension <- "pgdump"
  filename <- paste0(datestring, "_", "mars_data", ".", extension)
  filepath <- paste0("\\\\pwdoows\\oows\\Watershed Sciences\\GSI Monitoring\\07 Databases and Tracking Spreadsheets\\18 MARS Database Back Up Files\\PG 14\\", filename)
  filepath <- shQuote(filepath)
  pg_dump <- "C:\\Program Files\\pgAdmin 4\\v6\\runtime\\pg_dump.exe"
  pg_dump <- shQuote(pg_dump)
  host <- "PWDOOWSDBS"
  host <- shQuote(host)
  port <- "5434" 
  port <- shQuote(port)
  username <- "mars_admin"
  username <- shQuote(username)
  role <- "mars_admin"
  role <- shQuote(role)
  
  
#Assemble the entire pg_dump string	
  pgdumpstring <- paste(pg_dump,
                        "--file",filepath,
                        "--host",host,
                        "--port", port,
                        "--username",username,
                        "--no-password",
                        "--role",role,
                        format,
                        db)
 # run the command line using system function 
  results_dump <- system(pgdumpstring, intern = TRUE, wait = FALSE)

```


The `r params$database` database was `r ifelse(length(results_dump) == 0, "SUCCESSFULLY", "NOT")` backed up.`r if(length(results_dump) == 0){ paste("The file is located at", gsub("\\\\", "/", filepath)) }`

```{r Section 2 - Create Test DB, include = FALSE}	

## Create a database to host the test DB  

  #create db
  #testdbname <- paste(database_archive,"_","archivetest_",datestring, sep = "") longnames don't get recognize by pg_restore
  con <- odbc::dbConnect(odbc::odbc(), params$database)

  error_db <- NULL
  tryCatch({
    
    testdatabase <- paste("db",Sys.time() %>% format("%Y%m%d"), sep = "_")
    query_str <- "CREATE DATABASE %s WITH TEMPLATE = template0 OWNER = mars_admin"
    sql_query <- paste(sprintf(query_str,testdatabase),collapse="")
    results_createdb <- dbSendQuery(con, sql_query)
  
  },error=function(e){
  error_db <<- toString(conditionMessage(e))
    }
  )
  
  dbDisconnect(con)

```
 

```{r Section 3 - Restoring the  backup, include = FALSE}	

## Restore the archive
  
  pg_restore <- "C:\\Program Files\\pgAdmin 4\\v6\\runtime\\pg_restore.exe"
  pg_restore <- shQuote(pg_restore)
  
  #Assemble the entire pg_restore string	
  pgrestorestring <- paste(pg_restore,
                        "--host",host,
                        "--port", port,
                        "--username",username,
                        "--no-password",
                        "--role",role,
                        "--jobs=5",
                        paste("--dbname=",shQuote(testdatabase), sep=""),
                        filepath)
  results_restore <- system(pgrestorestring, intern = TRUE, wait = FALSE)
  
```

The scratch database was `r ifelse(is.null(error_db), "SUCCESSFULLY", "NOT")` created on the MARS postgres server. `r if(is.null(error_db)){ paste("The database is named", testdatabase) }`  
  
The scratch database was `r ifelse(length(results_restore) == 0, "SUCCESSFULLY", "NOT")` populated by the database archive located at `r gsub("\\\\", "/", filepath)`


```{r Section 4 - Prune old backups, include = FALSE}	
 
 ## Pruning old back ups
  #get a list of backup files  from the backup directory
  backups <- list.files("\\\\pwdoows\\oows\\Watershed Sciences\\GSI Monitoring\\07 Databases and Tracking Spreadsheets\\18 MARS Database Back Up Files\\PG 14")
  backup_pathway <- paste("\\\\pwdoows\\oows\\Watershed Sciences\\GSI Monitoring\\07 Databases and Tracking Spreadsheets\\18 MARS Database Back Up Files\\PG 14", backups, sep = "\\")
  
  #extract the backup date from the backup name and reformat it as Date
  backup_datestrings <- str_trunc(backups,8, "right", ellipsis = "")
  Dates <- as.Date(backup_datestrings, format="%Y%m%d")
  
  #add the weekdays
  backup_dates <-as.data.frame(Dates)
  backup_dates$W_Days <- weekdays(backup_dates$Dates)
  backup_dates$M_Days<- day(backup_dates$Dates)
  backup_dates$Days_Ago <- as.Date(Sys.time() %>% format("%Y-%m-%d"))-backup_dates$Dates
  backup_dates$M_number <- backup_dates$Dates %>%
    format("%Y-%m")
  
  #Count how many back up exist in each month-this is to prevent deleting the only back up existing for a month 
  backup_count <- backup_dates %>% 
    group_by(M_number) %>% 
    summarise(M_count = n())
  
  #join the count to the back up dataframe
  backup_dates <- backup_dates %>%
    inner_join(backup_count, by="M_number")
  
  #get index of those rows that are older than 7 days, and are not day 28 or Friday
  delete_lastmonth <- which(backup_dates$Days_Ago > 6 & backup_dates$Days_Ago < 30 & backup_dates$W_Days !="Friday" & backup_dates$M_Days !=28)
  #note the backup_dates$count !=1 condition (making sure we have at least one back up per month)
  delete_older <- which(backup_dates$Days_Ago > 29 & backup_dates$M_Days !=28 & backup_dates$M_count !=1)
  
  #prune the delete index 
  removed_files <- ifelse(length(c(delete_lastmonth,delete_older)) > 0,
                          paste(backups[c(delete_lastmonth,delete_older)], collapse = ", "), NA)
  results_prune <- file.remove(backup_pathway[c(delete_lastmonth,delete_older)])
  
```


```{r Section 5 - Log Table, include = FALSE}	

# DB
  con <- odbc::dbConnect(odbc::odbc(), params$database)
  time_stamp <- Sys.time()
  success <- c(ifelse(length(results_dump) == 0,TRUE,FALSE),
                                       ifelse(length(results_restore) == 0 & is.null(error_db),TRUE,FALSE),
                                       ifelse(length(results_prune) != 0, TRUE,FALSE))
  
  error <- c(ifelse(length(results_dump) == 0, NA, results_dump),
             ifelse(length(results_restore) == 0 & is.null(error_db), NA, paste(results_restore, error_db)),
             ifelse(length(results_prune) != 0, NA,"No back up file was deleted!"))
  
  pruned_files <- c(NA, NA, removed_files)
  
  record_log <- data.frame(operation = c("backup","restore","prune"),
                           success = success,
                           time = c(time_stamp,time_stamp,time_stamp),
                           error = error,
                           backup_path = c(filepath,filepath,filepath),
                           pruned_files)
                           
  dbWriteTable(con, SQL("admin.tbl_backup_logs"), record_log, append= TRUE, row.names = FALSE)
  dbDisconnect(con)
  
```

The back/restore/prune activities are summarised below and written to "admin.tbl_backup_logs":

```{r Section 6 - Log Table peek,echo=FALSE, results='asis'}	
    kable(record_log, caption = "Log Table")

```