---
title: "Worker Script: Update Plan Review Tables"
author: "Taylor Heffernan, Brian Cruice"
date: "11/10/2021"
output: html_document
params:
  database: "mars14_datav2" #Requires a DSN of the same name
  write: FALSE #Write Changes to database?
---

```{r Section 0.1 Setup and DB connections, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#libraries

#database packages
library(odbc)

#data manipulation packages
library(tidyverse)

#hashing packages
library(digest)


#db connections 

planreview <- dbConnect(odbc(), 
                        Driver = "ODBC Driver 17 for SQL Server", 
                        Server = "PWDSPRA", 
                        Database = "SPRA_ReportingDB", 
                        uid = 'GISREAD ', 
                        pwd = 'GISREAD ')


mars_data <- dbConnect(odbc(), params$database)
```



```{r Section 1: Querrying and Hashing, echo=FALSE}

#Query plan review tables
view_smp_designation <- dbGetQuery(planreview, "select * from View_SMP_Designation")

crosstab <- dbGetQuery(planreview, "select * from view_smpsummary_crosstab_asbuiltall") %>% select(-Depaving)

#Hash plan view tables
view_smp_designation_hash <- view_smp_designation %>% 
    rowwise() %>% 
    mutate("hash_md5" = digest(paste(`ProjectID`, `TrackingNumber`,  `SMPID`, `Designation`, `ProgramType`, `OOWProgramType`, `SMIP`, `GARP`), algo = "md5")) 
  
  crosstab_hash <- crosstab %>% 
    rowwise() %>% 
    mutate("hash_md5" = digest(paste(	`ProjectID`, `TrackingNumber`, `Projectname`, `SMPID`, `SMPType`, `Plan Label`, `Total Drainage Area`, `DCIA`, `Footprint`, `Loading Ratio`, `System Type`, `Location`, `Stone Storage Depth`, `Underdrain`, `Depth of Medium`, `Other - Pretreatment 1`, `Slow Release Volume`, `Static Storage`, `Water Quality Volume`, `Storage Material`, `Porous Material`, `Management Type`, `WQ Release Rate`, `Test Infiltration Rate`, `Orifice Diameter`, `Proprietary Rate Control`, `Effective Head`, `Drains To`, `Non-Regs`, `Brand Name`, `System Count`, `Rated WQ Flow Rate`, `CF Per Day`, `Tank Volume`, `Water Use`, `SW Credit`, `Total Pavement Disconnections`, `Existing Tree Credit Area`, `Number of New Trees`, `New Tree Credit Area`, `Planter Area`, `Number of Planters`, `Rooftop Area Disconnected`, `Confirmed`, `Last Modified By:`, `Date Modified:`), algo = "md5"))

#Query mars database
view_smp_designation_md <- dbGetQuery(mars_data, "select * from external.planreview_view_smp_designation")
  
crosstab_md <- dbGetQuery(mars_data, "select * from external.planreview_view_smpsummary_crosstab_asbuiltall")


  
#Logical test if queries were successful
query_test <- (nrow(view_smp_designation > 0) & nrow(crosstab > 0))
query_test_md <- (nrow(view_smp_designation_md > 0) & nrow(crosstab_md > 0))



```

#### The script has `r if(query_test & query_test_md){"successfully connected"}else{"not successfully connected"}` to the databases.

There are `r nrow(view_smp_designation)` records in the `View_SMP_Designation` table of `PWD_SWTracking` and `r nrow(view_smp_designation_md)` records in the `external.planreivew_view_smp_designation` table within `mars_data`. 

There are `r nrow(crosstab)` records in the `view_smpsummary_crosstab_asbuiltall` table of `PWD_SWTracking` and `r nrow(crosstab_md)` records in the `external.planreview_view_smpsummary_crosstab_asbuiltall` table within `mars_data`. 

```{r Section 2: Trimming, Joining, and Writing, echo = FALSE}

#Trimming dataframes
view_smp_designation_md_trim <- view_smp_designation_md %>% 
    dplyr::select(planreview_view_smp_designation_uid, `SMPID`)

crosstab_md_trim <- crosstab_md %>% 
  dplyr::select(planreview_view_smpsummary_crosstab_asbuiltall_uid, `SMPID`)

#New hashes
#smp designation
new_smp_hashes <- view_smp_designation_hash %>% 
  left_join(view_smp_designation_md_trim, by = "SMPID") %>% 
  anti_join(view_smp_designation_md, by = c("SMPID", "hash_md5"))
  
#system
new_crosstab_hashes <- crosstab_hash %>%
  left_join(crosstab_md_trim, by = "SMPID") %>%
  anti_join(crosstab_md, by = c("SMPID", "hash_md5")) 

#Write to mars_data
if(params$write){
  #write update query-----
  update_smp <- dbSendQuery(mars_data, 'update external.planreview_view_smp_designation set ProjectID=?, TrackingNumber=?,  SMPID=?, Designation=?, ProgramType=?, OOWProgramType=?, SMIP=?, GARP=?, hash_md5=? WHERE planreview_view_smp_designation_uid=?')
  
  #send the updated data
  dbBind(update_smp, new_smp_hashes)
  
  #release the prepared statement
  dbClearResult(update_smp)
  
  #crosstab-----
  
  #write update query
  update_crosstab <- dbSendQuery(mars_data, 'update external.planreview_view_smpsummary_crosstab_asbuiltall set "ProjectID"=?, "TrackingNumber"=?, "Projectname"=?, "SMPID"=?, "SMPType"=?, "Plan Label"=?, "Total Drainage Area"=?, "DCIA"=?, "Footprint"=?, "Loading Ratio"=?, "System Type"=?, "Location"=?, "Stone Storage Depth"=?, "Underdrain"=?, "Depth of Medium"=?, "Other - Pretreatment 1"=?, "Slow Release Volume"=?, "Static Storage"=?, "Water Quality Volume"=?, "Storage Material"=?, "Porous Material"=?, "Management Type"=?, "WQ Release Rate"=?, "Test Infiltration Rate"=?, "Orifice Diameter"=?, "Proprietary Rate Control"=?, "Effective Head"=?, "Drains To"=?, "Non-Regs"=?, "Brand Name"=?, "System Count"=?, "Rated WQ Flow Rate"=?, "CF Per Day"=?, "Tank Volume"=?, "Water Use"=?, "SW Credit"=?, "Total Pavement Disconnections"=?, "Existing Tree Credit Area"=?, "Number of New Trees"=?, "New Tree Credit Area"=?, "Planter Area"=?, "Number of Planters"=?, "Rooftop Area Disconnected"=?, "Confirmed"=?, "Last Modified By:"=?, "Date Modified:", hash_md5=? where planreview_view_smpsummary_crosstab_asbuiltall_uid=?')
  
  # send the updated data
  dbBind(update_crosstab, new_crosstab_hashes)
  
  #release the prepared statement
  dbClearResult(update_crosstab)
  
}
```

### The following `r nrow(new_smp_hashes)` records have `r if(!params$write){"not"}` been added to the `external.planreivew_view_smp_designation` table within `mars_data`:
`r if(nrow(new_smp_hashes)>0){knitr::kable(new_smp_hashes, caption = "New SMPs")}`

### The following `r nrow(new_crosstab_hashes)` records have `r if(!params$write){"not"}` been added to the `external.planreview_view_smpsummary_crosstab_asbuiltall` table within `mars_data`:
`r if(nrow(new_crosstab_hashes)>0){knitr::kable(new_crosstab_hashes, caption = "New Systems")}`

```{r Section3: Clean Up Connections and Render This HTML Document, include = FALSE}

dbDisconnect(planreview)
dbDisconnect(mars_data)

```
