---
title: "Worker Script Report: Update SMP Tables"
author:
- Taylor Heffernan
- Updating SMP Metadata Tables
date: "`r lubridate::now()`"
output: html_document
---

```{r setup, include=FALSE}

#GIS stuff
library(rgdal)
library(sf)

#Dplyr stuff
library(magrittr)
library(tidyverse)

#Database Stuff
library(odbc)

#Other stuff
library(knitr)
options(stringsAsFactors=FALSE)

```

```{r Section 0 - Preamble and database connections, include=FALSE}
###Section 0.1: Check parameter validity

#ODBC String for GIS DB
dsn_infra_pub <- paste0("MSSQL:server=PWDGISSQL;",
                          "database=GIS_APPS;",
                          "UID=gisread;",
                          "PWD=gisread;")

###Section 0.2: Connect to the database.
	marsDBCon <- dbConnect(odbc::odbc(), "mars_data14")

errorCodes <- data.frame(code = 0:4,
  message = c("Execution successful.",
              "Could not connect to Postgres. Is the database down?",
              NA, #Write error from TryCatch will be used
              NA, #Write error from TryCatch will be used
              NA #Write error from TryCatch will be used
               ), stringsAsFactors=FALSE)

keepRunning = TRUE
success = FALSE
errorCode = 0

#################################
####Error check - Did we connect?
#################################
if(!odbc::dbIsValid(marsDBCon))
{
  keepRunning = FALSE
  errorCode = 1
}

#Refresh materialized view so it has the newest cache of SMP IDs
#If we don't do this, new IDs won't be found, and we will get an insertion error.
if(keepRunning){
	dbGetQuery(marsDBCon, "REFRESH MATERIALIZED VIEW external.mat_assets WITH DATA;")
}
  

	
```
  
This script is attempting to update the `admin.tbl_smp_loc`, `admin.tbl_smp_radar`, and `admin.tbl_smp_gage` tables in the PG14 database. It grabs the WGS1984 SMP polygons from the `INFRASTRUCTURE_PUBLIC` database on PWDGIS4, converts them to centroids, and stores them in the `admin.tbl_smp_loc` table. It then checks the `smp_id`s contained in that table to see if any don't exist in `admin.tbl_smp_gage`. If they don't, it calculates which rain gage is closest to that SMP's centroid. Finally, it repeats this process with radar grid cells. Radar grid cells are also stored as grid cell centroids.

```{r Section 1 - Gathering data for the smp_loc table, include = FALSE, eval = keepRunning}
###Section 1: Update smp_loc table
###Check GIS data for any new SMPs, and insert them into smp_loc
	#Fetch current version of smp_loc
	smp_loc <- dbGetQuery(marsDBCon, "SELECT * FROM admin.tbl_smp_loc")
	smp_loc$lon_wgs84 %>% as.numeric %>% round(4) -> smp_loc$lon_wgs84
	smp_loc$lat_wgs84 %>% as.numeric %>% round(4) -> smp_loc$lat_wgs84
	
	#Grab centroids of new SMPs
	basin <- suppressWarnings((st_read(dsn_infra_pub, "gisad.GSWIBASIN", quiet = TRUE))) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	blueroof <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWIBLUEROOF_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	bumpout <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWIBUMPOUT_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	cistern <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWICISTERN_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	drainagewell <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWIDRAINAGEWELL_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	greenroof <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWIGREENROOF_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	permeablepavement <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWIPERMEABLEPAVEMENT_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	planter <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWIPLANTER_WGS84", quiet = TRUE)) %>% 
  	st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	raingarden <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWIRAINGARDEN_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	swale <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWISWALE_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	treetrench <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWITREETRENCH_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	trench <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWITRENCH_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	wetland <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWIWETLAND_WGS84", quiet = TRUE)) %>% 
	  st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
	  st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
	  filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
	  filter(!(smp_id %in% smp_loc$smp_id)) %>%
	  {data.frame(st_coordinates(.), .$smp_id)} %>%
	  select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)

	#Stick them all together
	smp_locNewData <- bind_rows(basin, blueroof, bumpout, cistern, drainagewell, greenroof, permeablepavement, planter, raingarden, swale, treetrench, trench, wetland)
	row.names(smp_locNewData) <- NULL
	
	if(nrow(smp_locNewData) == 0){
	  keepRunning = FALSE
	  success = TRUE
	}

```


```{r Section 1.5 - Writing to the smp_loc table, echo = FALSE, eval = all(keepRunning, nrow(smp_locNewData) > 0) }	
    knitr::asis_output(paste0("### New centroids to add to `admin.tbl_smp_loc`: ",  nrow(smp_locNewData)))

    kable(head(smp_locNewData))

    tryCatch(

      expr = {
        dbWriteTable(marsDBCon, 
          DBI::SQL("admin.tbl_smp_loc"), 
          smp_locNewData, 
          append= TRUE, 
          row.names = FALSE)
        success <<- TRUE
        },
      error = function(e) {
        keepRunning <<- FALSE
        errorCode <<- 2
        errorCodes$message[errorCode+1] <<- e$message #Error object is a list
      }
    )
```

```{r Section 2 - Gathering data for the smp_gage table, include = FALSE, eval = keepRunning}
###Section 2: Update smp_gage table
###If there are any SMPs with locations that do not have rain gage associations, apply those now
	#Read table of SMP locations (in case it got updated in step 1)
	smp_loc <- dbGetQuery(marsDBCon, "SELECT * FROM admin.tbl_smp_loc")

	#Read table of SMP/rain gage associations
	smp_gage <- dbGetQuery(marsDBCon, "SELECT * FROM admin.tbl_smp_gage")

	#Every SMP with a location should also have a rain gage. Find the ones that don't
	smp_loc_nogage <- anti_join(smp_loc, smp_gage, by = "smp_id")

	#If any SMPs don't have a gage
	if(nrow(smp_loc_nogage) > 0){
		#Fetch the rain gage locations from the database
		gage_loc <- dbGetQuery(marsDBCon, "SELECT * FROM admin.tbl_gage_loc")
		
		#Create spatial data frames for SMPs and gages
		gage_loc_spatial <- st_as_sf(gage_loc, coords = c(3, 4))
		nogage_spatial <- st_as_sf(smp_loc_nogage, coords = c(3, 4))
		
		#Find nearest gage for new SMPs
		smp_loc_nogage <- data.frame(smp_id = nogage_spatial$smp_id, 
		                             gageindex = st_nearest_feature(nogage_spatial, gage_loc_spatial)) %>%
		  mutate(gage_uid = gage_loc_spatial$gage_uid[gageindex]) %>%
		  filter(!duplicated(smp_id)) %>%
		  select(smp_id, gage_uid)
	}
```


```{r Section 2.5 - Writing to the smp_gage table, echo = FALSE, eval = all(keepRunning, nrow(smp_loc_nogage) > 0)}
    knitr::asis_output(paste0("### New gage associations in `admin.tbl_smp_gage`: ",  nrow(smp_loc_nogage)))

    kable(head(smp_loc_nogage))

    tryCatch(

      expr = {
        dbWriteTable(marsDBCon, 
          DBI::SQL("admin.tbl_smp_gage"), 
          smp_loc_nogage, 
          append= TRUE, 
          row.names = FALSE)
        success <<- TRUE
        },
      error = function(e) {
        keepRunning <<- FALSE
        errorCode <<- 3
        errorCodes$message[errorCode+1] <<- e$message #Error object is a list
      }
    )
```

```{r Section 3 - Gathering data for the smp_radar table, include = FALSE}
###Section 3: Update smp_radar table
###If there are any SMPs with locations that do not have radar associations, apply those now
	#Read table of SMP locations (in case it got updated in step 1)
	smp_loc <- dbGetQuery(marsDBCon, "SELECT * FROM admin.tbl_smp_loc")

	#Read table of SMP/radar associations
	smp_radar <- dbGetQuery(marsDBCon, "SELECT * FROM admin.tbl_smp_radar")

	#Every SMP with a location should also have a radar. Find the ones that don't
	smp_loc_noradar <- anti_join(smp_loc, smp_radar, by = "smp_id")

	#If any SMPs don't have a radar
	if(nrow(smp_loc_noradar) > 0){
		#Fetch the radar locations from the database
		radar_loc <- dbGetQuery(marsDBCon, "SELECT * FROM admin.tbl_radar_loc")
		
		#Create spatial data frames for SMPs and radars
		radar_loc_spatial <- st_as_sf(radar_loc, coords = c(3, 4))
		noradar_spatial <- st_as_sf(smp_loc_noradar, coords = c(3, 4))
		
		#Find nearest radar for new SMPs
		smp_loc_noradar <- data.frame(smp_id = noradar_spatial$smp_id, 
		                             radarindex = st_nearest_feature(noradar_spatial, radar_loc_spatial)) %>%
		  mutate(radar_uid = radar_loc_spatial$radar_uid[radarindex]) %>%
		  select(smp_id, radar_uid)
	}
```

```{r Section 3.5 - Writing to the smp_radar table, echo = FALSE, eval = all(keepRunning, nrow(smp_loc_noradar) > 0)}
    knitr::asis_output(paste0("### New radar associations in `admin.tbl_smp_radar`: ",  nrow(smp_loc_noradar)))

    kable(head(smp_loc_noradar))

    tryCatch(

      expr = {
        dbWriteTable(marsDBCon, 
          DBI::SQL("admin.tbl_smp_radar"), 
          smp_loc_noradar, 
          append= TRUE, 
          row.names = FALSE)
        success <<- TRUE
        },
      error = function(e) {
        keepRunning <<- FALSE
        errorCode <<- 4
        errorCodes$message[errorCode+1] <<- e$message #Error object is a list
      }
    )
```

# Script Results: `r ifelse(keepRunning, "SUCCESS", ifelse(success, "SUCCESS", "FAILURE"))`
## Exit Code: `r errorCode`
## Exit Message: `r errorCodes$message[errorCode+1]`

```{r Section 4 - Close DB connections and render this file, include = FALSE}
	#Close database connections
	dbDisconnect(marsDBCon)
```
