---
title: "Worker Script Report: Update SMP Tables"
author:
- Taylor Heffernan
- Updating smp_loc and smp_gage
date: "`r lubridate::now()`"
output: html_document
params:
  file: "A:/Scripts/Maintenance/update_smp_tables/centroids_folder/centroids_dem_20190408T1300.shp" #ESRI shapefile containing SMP centroids
  database: "mars_testing" #One of mars or mars_testing. Requires a DSN of the same name.
  write: FALSE #Write changes to database?
---

```{r setup, include=FALSE}

#GIS stuff
library(rgdal)
library(rgeos)

#Dplyr stuff
library(magrittr)
library(tidyverse)

#Database Stuff
library(odbc)

#Other stuff
library(knitr)
options(stringsAsFactors=FALSE)

```

```{r Section 0 - Preamble and database connections, include=FALSE}
###Section 0.1: Check parameter validity
	if(is.na(params$file)){
		stop("No file specified. In the rmarkdown::render call, specify the ESRI shapefile containing centroids with file = FILEPATH")
	}

###Section 0.2: Connect to the database
	#Indicate the database name: mars_testing or mars. 
	#Only write to mars if you really know what you're doing.
 	database <- params$database

 	#Connect using the DSN.
	marsDBCon <- dbConnect(odbc::odbc(), database)
 	
 	#This is required to append new data to database tables
	if(params$write == TRUE){

		#Refresh materialized view so it has the newest cache of SMP IDs
		#If we don't do this, new IDs won't be found, and we will get an insertion error.
		dbGetQuery(marsDBCon, "REFRESH MATERIALIZED VIEW smpid_facilityid_componentid WITH DATA;")
	}

```
  
This script is attempting to update the `smp_loc` and `smp_gage` tables in the `r params$database` database. It inhales the centroids previously exported by the `arcpy_centroids_export.py` script, and stores them in the smp_loc table. It then checks the `smp_id`s contained in `smp_loc` to see if any don't exist in `smp_gage`. If they don't, it calculates which rain gage is closest to that SMP's centroid. Finally, it checks the elevation of each SMP as reported by intersecting the centroid with the raster DEM, and appends new elevations to the `smp_elev` table.

```{r Section 1 - Gathering data for the smp_loc table, include = FALSE}
###Section 1: Update smp_loc table
###Check GIS data for any new SMPs, and insert them into smp_loc
	#Fetch current version of smp_loc
	smp_loc <- dbGetQuery(marsDBCon, "SELECT * FROM smp_loc")
	smp_loc$lon_wgs84 %>% as.numeric %>% round(4) -> smp_loc$lon_wgs84
	smp_loc$lat_wgs84 %>% as.numeric %>% round(4) -> smp_loc$lat_wgs84

	#File path containing ESRI Shapefile of SMP centroids
	gis_path_SMP <- params$file
	# gis_path_SMP <- "//pwdoows/oows/Watershed Sicences/GSI Monitoring/06 Special Projects/24 MARS Database files/Worker Scripts/update_smp_tables/centroids_folder/centroids_20181207.shp"
	gis_layer_SMP <- basename(gis_path_SMP) %>% {gsub("\\.shp$", "", .)}

	#TODO: Data Validation on GIS data
	#Centroids and not polygons
	#@data contains "SMP_ID" field
	
	#Read shapefile and translate to WGS1984 unprojected coordinate system
	smp_shapefile <- readOGR(dsn = gis_path_SMP, layer = gis_layer_SMP) #read shapefile
	smp_data <- spTransform(smp_shapefile , CRS('+init=epsg:4326')) # spatial trasnformation to unprojected WGS1984 coordinate system

	smp.coords <- as.data.frame(smp_data@coords) %>% # set data type to a data frame object
		mutate(smp_id = as.character(smp_data$SMP_ID), # smp_id to character class type
			lon_wgs84 = round(coords.x1,4),         # limit cooridnates to 4 digit place
			lat_wgs84 = round(coords.x2,4)) %>% 
		na.omit() %>% # delete all missing data
		select(smp_id, lon_wgs84, lat_wgs84) %>% # Remove raw coordinate columns
		distinct(smp_id, .keep_all = TRUE) # remove duplicate smp_ids

	#Scrub the data frame of whitespace and row names
	smp.coords$smp_id <- gsub("\\s","", smp.coords$smp_id) # remove empty white spaces from smp id column 
	row.names(smp.coords) <- NULL # row names reset to NULL, to keep row names same as row numbers

	#Perform an anti-join to see if any new SMPs exist
	smp_locNewData <- anti_join(smp.coords, smp_loc, by = c("smp_id")) #assign only the new rows to the object that will go into the table

```


## Updates to `smp_loc` Table

New centroids have been exported and examined against the existing `smp_loc` table. There are `r nrow(smp_locNewData)` new centroids to add to the `smp_loc` table.

`r if(nrow(smp_locNewData) > 0){knitr::kable(smp_locNewData)}`

```{r Section 1.5 - Writing to the smp_loc table, include = FALSE}	
  #Fail safe. If the block below doesn't run, we didn't append anything
  outcome_centroids <- FALSE

  #If there's new data to append
	if(nrow(smp_locNewData) > 0 & params$write == TRUE){
    tryCatch({outcome_centroids <- dbWriteTable(marsDBCon, "smp_loc", smp_locNewData, append= TRUE, row.names = FALSE)}, # append the data
             error = function(e) e
    )
  }
```

New centroids have `r ifelse(outcome_centroids, "SUCCESSFULLY", "NOT")` been appended to the `smp_loc` table.

---  

```{r Section 2 - Gathering data for the smp_gage table, include = FALSE}
###Section 2: Update smp_gage table
###If there are any SMPs with locations that do not have rain gage associations, apply those now
	#Read table of SMP locations (in case it got updated in step 1)
	smp_loc <- dbGetQuery(marsDBCon, "SELECT * FROM smp_loc")

	#Read table of SMP/rain gage associations
	smp_gage <- dbGetQuery(marsDBCon, "SELECT * FROM smp_gage")

	#Every SMP with a location should also have a rain gage. Find the ones that don't
	smp_loc_nogage <- anti_join(smp_loc, smp_gage, by = "smp_id")

	#If any SMPs don't have a gage
	if(nrow(smp_loc_nogage) > 0){
		#Fetch the rain gage locations from the database
		gage_loc <- dbGetQuery(marsDBCon, "SELECT * FROM gage_loc")

		#Convert lat/long coordinates to numeric form
		smp_loc_nogage$lon_wgs84 <- as.numeric(smp_loc_nogage$lon_wgs84)
		smp_loc_nogage$lat_wgs84 <- as.numeric(smp_loc_nogage$lat_wgs84)
		gage_loc$lon_wgs84 <- as.numeric(gage_loc$lon_wgs84)
		gage_loc$lat_wgs84 <- as.numeric(gage_loc$lat_wgs84)

		#Create spatial data frames for SMPs and gages
		smp_loc_nogage_spatial <- smp_loc_nogage
		coordinates(smp_loc_nogage_spatial) <- c("lon_wgs84", "lat_wgs84")
		coordinates(gage_loc) <- c("lon_wgs84", "lat_wgs84")

		#Find the closest gage to each SMP without a gage
		#Note: which.min will return the INDEX of the closest gage, not its gage_uid
			#ie if the closest gage is the 4th one on the list, it will return 4
			#If gage_loc isn't sorted by increasing gage_uid, point 4 might not correspond to gage_uid 4!
			#To guard against improperly assigning gages in this way, we will use this index to extract the real gage_uid from gage_loc in the next step
		#https://stackoverflow.com/questions/27442506/find-nearest-points-of-latitude-and-longitude-from-different-data-sets-with-diff
		smp_loc_nogage_spatial$closestgageindex <- apply(gDistance(gage_loc, smp_loc_nogage_spatial, byid=TRUE), 1, which.min)

		#Use this index to find the corresponding gage_uids
		#If gage_loc was sorted by increasing gage_uid in the previous step, these numbers will be the same
		#But if it wasn't, then we need to do this to find the real gage_uids
		smp_loc_nogage_spatial$gage_uid <- gage_loc$gage_uid[smp_loc_nogage_spatial$closestgageindex]

		#Remove the columns that don't belong in the smp_gage table
		smp_loc_nogage <- select(smp_loc_nogage_spatial@data, smp_id, gage_uid)
	}
```

## Updates to `smp_gage` Table

The `smp_gage` table has been checked for SMPs without a rain gage association. There are `r nrow(smp_loc_nogage)` new entries to add to the `smp_gage` table.

`r if(nrow(smp_loc_nogage) > 0){knitr::kable(smp_loc_nogage)}`

```{r Section 2.5 - Writing to the smp_gage table, include = FALSE}
    #Fail safe. If the block below doesn't run, we didn't append anything
	outcome_gage <- FALSE

	#If there's new data to append
    if(nrow(smp_loc_nogage) > 0 & params$write == TRUE){
		  tryCatch({outcome_gage <- dbWriteTable(marsDBCon, "smp_gage", smp_loc_nogage, append= TRUE, row.names = FALSE)}, # append the data	
		           error = function(e) e
		  )
	  }
```

New gage associations have `r ifelse(outcome_gage, "SUCCESSFULLY", "NOT")` been appended to the `smp_gage` table.  

---

```{r Section 3 - Gathering data for the smp_elev table, include = FALSE}
	
	#Read existing SMP elev table
	smp_elev <- dbGetQuery(marsDBCon, "select * from smp_elev")

	#Create data frame of SMP IDs and DEM values
	smp_fileelev <- smp_shapefile@data %>%
		select(smp_id = gsub("\\s","", "SMP_ID"), elev_ft = RASTERVALU) %>%
		filter(complete.cases(.))

	#Which ones are new?
	smp_elevNewData <- anti_join(smp_fileelev, smp_elev, by = "smp_id") %>%
	  filter(!duplicated(smp_id)) #In case any SMPs are multiple distinct polygons


```


## Updates to `smp_elev` Table

New centroids have been intersected with the DEM and examined against the existing `smp_elev` table. There are `r nrow(smp_elevNewData)` new centroids to add to the `smp_elev` table.

`r if(nrow(smp_elevNewData) > 0){knitr::kable(smp_elevNewData)}`

```{r Section 3.5 - Writing to the smp_elev table, include = FALSE}	
  #Fail safe. If the block below doesn't run, we didn't append anything
  outcome_elevations <- FALSE

  #If there's new data to append
	if(nrow(smp_elevNewData) > 0 & params$write == TRUE){
    tryCatch({outcome_elevations <- dbWriteTable(marsDBCon, "smp_elev", smp_elevNewData, append= TRUE, row.names = FALSE)}, # append the data
             error = function(e) e
    )
  }
```

New elevations have `r ifelse(outcome_elevations, "SUCCESSFULLY", "NOT")` been appended to the `smp_elev` table.

```{r Section 4 - Close DB connections and render this file, include = FALSE}
	#Close database connections
	dbDisconnect(marsDBCon)
```
