---
title: "Worker Script Report: Update OW Data"
author:
- Taylor Heffernan
- Updating ow_leveldata
date: "`r lubridate::now()`" 
output: html_document
params:
  database: "mars_testing" #One of mars or mars_testing. Requires a DSN of the same name.
  write: TRUE #Write changes to database?
---

```{r setup, include=FALSE}

#Dplyr stuff
library(magrittr)
library(tidyverse)
library(lubridate)

#Database Stuff
library(RODBC)
library(odbc)

#Other stuff
library(knitr)
options(stringsAsFactors=FALSE)
```

```{r Section 0 - Preamble and database connections, include=FALSE}
###Section 0.1: Check parameter validity

###Section 0.2: Connect to the database
	#Indicate the database name: mars_testing or mars. 
	#Only write to mars if you really know what you're doing.
 	database <- params$database

 	#Connect using the DSN.
	marsDBCon <- dbConnect(odbc::odbc(), params$database)
	
```

```{r Section 1A - Gathering OW data, include = FALSE}

  #Read the latest date from each observation well from the mars database
  ow_latestdates <- dbGetQuery(marsDBCon, "SELECT * FROM owdata_latestdates") %>%
    mutate(dtime_est = force_tz(dtime_est, tz = "EST")) #Adjust time zone without moving timestamp
  
  #Read the accessdb table from the mars database and attach it to the date data
  accessdb <- dbGetQuery(marsDBCon, "SELECT filepath, ow_uid, datatable, sumptable FROM accessdb")
  accessdb_latestdates <- left_join(ow_latestdates, accessdb, by = "ow_uid") %>% 
    filter(!is.na(filepath), !is.na(datatable))
  
  #Read the data from each Access DB's data table, 
  newdata <- data.frame(dtime_est = NULL, ow_uid = NULL, level_ft = NULL) #data frame to incrementally append to

  for(i in 1:nrow(accessdb_latestdates)){
    accessdbCon <- odbcConnectAccess2007(accessdb_latestdates$filepath[i])
    accessdb_latestdates$dtime_est[i][is.na(accessdb_latestdates$dtime_est[i])] <- mdy('2/20/2001', tz = "EST")
    accessdb_query <- paste0("select * from [", accessdb_latestdates$datatable[i], "] where [Standard Dtime] > #",accessdb_latestdates$dtime_est[i], "# ")
    print(accessdb_query)

    accessdb_newdata <- sqlQuery(accessdbCon, accessdb_query, as.is = TRUE) %>%
       select(dtime_est = 1, level_ft = ncol(.)) %>% #dtime is the first column, level is the last
       mutate(dtime_est = ymd_hms(dtime_est, tz = "EST"), level_ft = as.numeric(level_ft)) %>% #Data comes in as plain text from RODBC
       filter(dtime_est > accessdb_latestdates$dtime_est[i]) %>% #We still need to filter by > the latest date because Access will treat values with fractional seconds as > values without fractional seconds. When R recieves them, though, we get them without the fractional seconds, so from our perspective, we have a value that is = the latest date. This is very silly.
       arrange(dtime_est) %>% #Order by ascending datetime in case it's out of order in the DB
       mutate(ow_uid = accessdb_latestdates$ow_uid[i]) %>% #Attach OW UID to the data
       mutate(key = paste(ow_uid, dtime_est, sep = "_"), 
              dupe = duplicated(key)) %>% #Sometimes there are duplicates in the Access DBs
       filter(dupe == FALSE) %>% #Remove the dupe rows
       select(-key, -dupe) #Remove the key columns
       
    newdata <- bind_rows(newdata, accessdb_newdata)
    odbcClose(accessdbCon)
  }
  
  #Some nulls may exist so we purge them
  ##TODO: Report the number of NAs that get purged per OW UID in some manner, possibly if above a certain number of NAs.
  newdata %<>% filter(complete.cases(newdata))
  newdata$dtime_est <- newdata$dtime_est %>% 
    round_date(unit = "minute") %>%
    as.character

  #Pull OW table for use in the report table
  ow <- dbGetQuery(marsDBCon, "select * from fieldwork.ow_all")

```


## Updates to `ow_leveldata_raw` Table

The Access DBs for each observation well have been examined. There are `r nrow(newdata)` new measurements to add to the `ow_leveldata` table.

`r if(nrow(newdata) > 0){group_by(newdata, ow_uid) %>% summarize(firstdate_est = first(dtime_est), lastdate_est = last(dtime_est), n = n()) %>% left_join(accessdb, by = "ow_uid") %>% left_join(ow, by = "ow_uid") %>% select(smp_id, ow_suffix, firstdate_est, lastdate_est, n) %>% kable }`

```{r Section 1B - Writing to the ow_leveldata table, include = FALSE}	
# Fail safe. If the block below doesn't run, we didn't append anything
  outcome_newdata <- FALSE

  #If there's new data to append
	if(nrow(newdata) > 0 & params$write == TRUE){
    tryCatch({outcome_newdata <- dbWriteTable(marsDBCon,
        "ow_leveldata_raw",
        newdata,
        append= TRUE,
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }
```

`r if(nrow(newdata) > 0){ paste("New level data has", ifelse(outcome_newdata, "SUCCESSFULLY", "NOT"), "been written to the ow_leveldata table")}`

```{r Section 2A - Gathering GW data, include = FALSE}

  #Read the latest date from each observation well from the mars database
  gw_latestdates <- dbGetQuery(marsDBCon, "SELECT * FROM gwdata_latestdates") %>%
    mutate(dtime_est = force_tz(dtime_est, tz = "EST")) #Adjust time zone without moving timestamp
  
  #Read the accessdb table from the mars database and attach it to the date data
  accessdb <- dbGetQuery(marsDBCon, "SELECT filepath, ow_uid, datatable, sumptable FROM accessdb")
  accessdb_latestdates <- left_join(gw_latestdates, accessdb, by = "ow_uid") %>% filter(!is.na(filepath), !is.na(datatable))
  
  #Read the data from each Access DB's data table, 
  newdata <- data.frame(dtime_est = NULL, ow_uid = NULL, depth_ft = NULL) #data frame to incrementally append to

  for(i in 1:nrow(accessdb_latestdates)){
    accessdbCon <- odbcConnectAccess2007(accessdb_latestdates$filepath[i])
    accessdb_latestdates$dtime_est[i][is.na(accessdb_latestdates$dtime_est[i])] <- mdy('2/20/2001', tz = "EST") #replace NAs with an early date
    accessdb_query <- paste0("select * from [", accessdb_latestdates$datatable[i], "] where [Standard Dtime] > #",accessdb_latestdates$dtime_est[i], "# ") #query new rows

    accessdb_newdata <- sqlQuery(accessdbCon, accessdb_query, as.is = TRUE) %>% 
      select(dtime_est = 1, depth_ft = ncol(.)) %>% #dtime is the first column, level is the last
      mutate(dtime_est = ymd_hms(dtime_est), depth_ft = as.numeric(depth_ft)) %>% #Data comes in as plain text from RODBC
      filter(dtime_est > accessdb_latestdates$dtime_est[i]) %>% #Only take the new data
      arrange(dtime_est) %>% #Order by ascending datetime in case it's out of order in the DB
      mutate(ow_uid = accessdb_latestdates$ow_uid[i]) %>% #Attach OW UID to the data
      mutate(key = paste(ow_uid, dtime_est, sep = "_"), 
              dupe = duplicated(key)) %>% #Sometimes there are duplicates in the Access DBs
       filter(dupe == FALSE) %>% #Remove the dupe rows
       select(-key, -dupe) #Remove the key columns
      
    newdata <- bind_rows(newdata, accessdb_newdata)
    odbcClose(accessdbCon)
  }
  
  #Some nulls may exist so we purge them
  newdata %<>% filter(complete.cases(newdata))
  newdata$dtime_est <- newdata$dtime_est %>% 
    round_date(unit = "minute") %>%
    as.character

```


## Updates to `gw_leveldata` Table

The Access DBs for each groundwater well have been examined. There are `r nrow(newdata)` new measurements to add to the `gw_depthdata` table.

`r if(nrow(newdata) > 0){ group_by(newdata, ow_uid) %>% summarize(firstdate_est = first(dtime_est), lastdate_est = last(dtime_est), n = n()) %>% left_join(gw_latestdates) %>% select(smp_id, ow_suffix, firstdate_est, lastdate_est, n) %>% kable }`

```{r Section 2B - Writing to the gw_depthdata table, include = FALSE}	
# Fail safe. If the block below doesn't run, we didn't append anything
  outcome_newgwdata <- FALSE

  #If there's new data to append
	if(nrow(newdata) > 0 & params$write == TRUE){
    tryCatch({outcome_newgwdata <- dbWriteTable(marsDBCon, 
        "gw_depthdata_raw", 
        newdata, 
        append= TRUE, 
        row.names = FALSE)
      }, # append the data
      error = function(e) e
    )
  }
```

`r if(nrow(newdata) > 0){ paste("New depth data has", ifelse(outcome_newgwdata, "SUCCESSFULLY", "NOT"), "been written to the gw_depthdata table")}`


```{r Section 3 - Close DB connections and render this file, include = FALSE}
	#Close database connections
	dbDisconnect(marsDBCon)
```
